\documentclass[aps,prl,preprint,12pt]{revtex4}
\usepackage{CJK}
\usepackage{graphicx}
%\usepackage{authblk}

\begin{document}

\begin{CJK*}{GB}{}
\title{CLAS12 Track Reconstruction with Artificial Intelligence}

\author{Gagik Gavalian}
\affiliation{Jefferson Lab, Newport News, VA, USA}
\author{Polykarpos Thomadakis}
\author{Angelos Angelopoulos}
\affiliation{CRTC, Department of Computer Science, Old Dominion University, Norfolk, VA, USA}
\author{Raffaella De Vita}
\author{Veronique Ziegler}
\affiliation{Jefferson Lab, Newport News, VA 23606, USA}
\author{Nikos Chrisochoides}
\affiliation{CRTC, Department of Computer Science, Old Dominion University, Norfolk, VA, USA}

\begin{abstract}
  In this article we describe the implementation of Artificial Intelligence models in track reconstruction
  software for the CLAS12 detector at Jefferson Lab. The Artificial Intelligence based approach resulted 
  in improved track reconstruction efficiency in high luminosity experimental conditions.  The track
 reconstruction efficiency increased by $10-12\%$ for single particle, and statistics in multi-particle physics 
 reactions increased by $15\%-35\%$ depending on the number of particles in the reaction. The implementation 
 of artificial intelligence in the workflow also resulted in a speedup of the tracking by $35\%$. 
 % we estimated these 
 %improvements are equivalent of more than $\$4$M  annual savings for realization of the CLAS12 physics program.
\end{abstract}

\maketitle
\end{CJK*}

\section{Introduction}
\indent

Nuclear Physics experiments have become increasingly complex over the past decades, with more complex detector 
systems and higher luminosities. In emerging experiments where data collection rates are higher, there is a need for 
new approaches for data processing that can improve data reconstruction accuracy and speed. New developments in 
the Artificial Intelligence (AI) field present promising alternatives to conventional algorithms for data processing. 
Machine Learning (ML) algorithms are being employed in various stages of experimental data processing, such as: 
the detector data reconstruction, particle identification, detector simulations and physics analysis. 

In this paper we present the implementation of machine learning models into the CLAS12 charged-particle track 
reconstruction software. Detailed analysis of the reconstruction performance are presented, comparing track 
reconstruction efficiency and speed improvements to conventional algorithms.

%\section{CLAS12 experiments}

%To estimate the statistical accuracy of proposed experiments calculation are made to derive 
%best experimental conditions to achieve physics goals. One of the large experiments running 
%on CLAS12 detector is Deeply Virtual Compton Scattering (DVCS) rung group (RGA). The 
%estimations for experimental time were calculated assuming $100\%$ tracking efficiency at 
%$90~nA$ (equal to $L=2\times10^{35}~cm^{-2}sec^{-1}$) and was estimated that $80$ days
%of experimental time is needed to achieve the physics goals. However, the conventional tracking 
%algorithm does not perform as expected and can provide only $90\%$ tracking efficiency at $45~nA$
%incident beam energy. Currently experiments run at $45~nA$ (equivalent to 
%$L=1\times 10^{35}~cm^{-2}sec^{-1}$) which will only achieve half of desired statistical requirements
%of experiment. With use of Artificial Intelligence we intend reduce the discrepancy between experimental
%time and physics goals.

%************************************
%-------- Included Chapters
\input{particle_tracking}

\input{neural_networks}
\input{implementation}
\input{results}

\section{Acknowledgments}

This material is based upon work supported by the U.S. Department of Energy, Office of Science, Office of Nuclear 
Physics under contract DE-AC05-06OR23177, and NSF grant no. CCF-1439079 and the Richard T. Cheng Endowment. 
This  work  was  performed  using  the  Turing  and  Wahab computing clusters at Old Dominion University.
 
\newpage
\bibliography{references}
\bibliographystyle{ieeetr}



\end{document}
