\documentclass[preprint,12pt]{elsarticle}
\usepackage{graphicx}
\usepackage[margin=1.0in]{geometry}
\usepackage{color, colortbl}
\usepackage{hyperref}
\usepackage{float}
% \usepackage[affil-it]{authblk}
\usepackage{subcaption}
\newcommand{\note}[1]{\textcolor{blue}{#1}}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{LightRose}{rgb}{1,0.88,0.88}
\definecolor{LightGreen}{rgb}{0.88,1,0.88}

\title{CLAS12 Track Reconstruction With Artificial Intelligence }
\author[1]{Gagik Gavalian}
\author[2]{Polykarpos Thomadakis }
\author[2]{Angelos Angelopoulos}
\author[2]{Nikos Chrisochoides}
\author[1]{Raffella De Vita}
\author[1]{Veronique Ziegler}


% \affiliation[1]{organization={CRTC, Department of Computer Science, Old Dominion University}, city={Norfolk, VA}, country={USA}}
\address[1]{Jefferson Lab, Newport News, VA, USA}
\address[2]{CRTC, Department of Computer Science, Old Dominion University, Norfolk, VA, USA}
%Authored by Jefferson Science Associates, LLC under U.S. DOE Contract No. DE-AC05-06OR23177. The U.S. Government retains a non-exclusive, paid-up, irrevocable, world-wide license to publish or reproduce this manuscript for U.S. Government purposes.

%\fntext[fn1]{Authors contributed equally.}
%\fntext[fn2]{Correspoding author, \textit{gavalian@jlab.org}}


\begin{document}

%\begin{titlepage}

\begin{abstract}

  In this article we describe the implementation of Artificial Intelligence models in track reconstruction software for the CLAS12 detector at Jefferson Lab.
 The Artificial Intelligence based approach resulted in improved track reconstruction efficiency in high luminosity experimental conditions.  The track
 reconstruction efficiency increased by $15\%$ for single particle, and statistics in multi-particle physics reactions increased by $15\%-35\%$ depending 
 on the number of particles in the reaction. The implementation of artificial intelligence in the workflow also resulted in code speedup of $35\%$.
\end{abstract}
%\end{titlepage}
\maketitle


\section{Introduction}
\indent

Nuclear Physics experiments have become increasingly complex over the past decades, using higher beam energies and higher beam currents. In emerging experiments where data collection rates are higher there is a need for new approaches of data processing that can improve data reconstruction accuracy and speed. New developments in the Artificial Intelligence (AI) field present promising alternatives to conventional algorithms for data processing. Machine Learning (ML) algorithms are being employed in various stages of experimental data processing, such as: detector data reconstruction, particle identification, detector simulations and physics data analysis. 

In this paper we present the implementation of previously developed machine learning models into the CLAS12 track reconstruction software. Detailed analysis 
of the reconstruction performance presented comparing track reconstruction efficiency and speed improvements to conventional algorithms.


\input{particle_tracking}

\input{neural_networks}

\input{implementation}

\input{results}

\section{Acknowledgments}

This material is based upon work supported by the U.S. Department of Energy, Office of Science, Office of Nuclear Physics under contract DE-AC05-06OR23177, and
 %This research was sponsored in part from Jefferson Lab grant no. XXX, SURA grant No. CNF-19-04, 
 NSF grant no. CCF-1439079 and the Richard T. Cheng Endowment. The authors would like to thank Raffaella De Vita for help in processing data with CLAS12 reconstruction software. This  work  was  performed  using  the  Turing  and  Wahab computing clusters at Old Dominion University.
 
\newpage
\bibliography{references}
\bibliographystyle{ieeetr}

\end{document}
