\documentclass[preprint,12pt]{elsarticle}
\usepackage{graphicx}
\usepackage[margin=1.0in]{geometry}
\usepackage{color, colortbl}
\usepackage{hyperref}
\usepackage{float}
\usepackage{lineno}
\usepackage{tabularx} % For specifying table width
\usepackage{array}    % For additional column formatting options
%\linenumbers
% \usepackage[affil-it]{authblk}
\usepackage{subcaption}
\usepackage{listings}

\newcommand{\note}[1]{\textcolor{blue}{#1}}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{LightRose}{rgb}{1,0.88,0.88}
\definecolor{LightGreen}{rgb}{0.88,1,0.88}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\title{High-Performance Data Format for Scientific Data Storage and Analysis}

\author[1]{Gagik Gavalian}
\address[1]{Thomas Jefferson National Accelerator Facility, Newport News, VA, USA}

\begin{document}

%\begin{titlepage}
\begin{abstract}
In this article, we present the High-Performance Output (HiPO) data format developed at Jefferson Laboratory for 
storing and analyzing data from Nuclear Physics experiments. The format was designed to efficiently store large
amounts of experimental data, utilizing modern fast compression algorithms. The purpose of this development was 
to provide organized data in the output, facilitating access to relevant information within the large data files. The HiPO
data format has features that are suited for storing raw detector data, reconstruction data, and the final physics analysis 
data efficiently, eliminating the need to do data conversions through the lifecycle of experimental data. The HiPO data format
is implemented in C++ and JAVA, and provides bindings to FORTRAN, Python, and Julia, providing users with the choice of data 
analysis frameworks to use.
In this paper, we will present the general design and functionalities of the HiPO library and compare the performance of the library with
 more established data formats used in data analysis in High Energy and Nuclear Physics (such as ROOT and Parquete). In columnar data analysis, HiPO surpasses established data formats in performance and can be effectively applied to data analysis in other scientific fields.

\end{abstract}
%\end{titlepage}
\maketitle

\input{introduction}
\input{motivation}
\input{format}
\input{tagging}
\input{columnar}
\input{summary}

\section{Acknowledgments}

This material is based upon work supported by the U.S. Department of Energy, Office of Science,
Office of Nuclear Physics under contract DE-AC05-06OR23177, and NSF grant no. CCF-1439079 and
the Richard T. Cheng Endowment. 
 
 
\begin{thebibliography}{}
%\cite{Aplin:2012kj}
%\cite{CLAS:2003umf}
\bibitem{CLAS:2003umf}
B.~A.~Mecking \textit{et al.} [CLAS],
``The CEBAF Large Acceptance Spectrometer (CLAS),''
Nucl. Instrum. Meth. A \textbf{503} (2003), 513-553
doi:10.1016/S0168-9002(03)01001-5
\bibitem{Burkert:2020akg}
Burkert, V.D. and others, The CLAS12 Spectrometer at Jefferson Laboratory, Nucl. Instrum. Meth. A \textbf{959},163419 (2020)
\bibitem{Brun:1997pa}
R.~Brun and F.~Rademakers,
``ROOT: An object oriented data analysis framework,''
Nucl. Instrum. Meth. A \textbf{389} (1997), 81-86
doi:10.1016/S0168-9002(97)00048-X

\bibitem{Aplin:2012kj}
S.~Aplin, J.~Engels, F.~Gaede, N.~A.~Graf, T.~Johnson and J.~McCormick,
``LCIO: A Persistency Framework and Event Data Model for HEP,''
doi:10.1109/NSSMIC.2012.6551478

\bibitem{HDF5:2000pa}
The HDF Group,  http://www.hdfgroup.org/HDF5/

\bibitem{PARKQUET:2020jk}
Apache Parquet, https://parquet.apache.org

\bibitem{hipo5p0:2025jk}
The HiPO Group, 
https://github.com/gavalian/hipo
\end{thebibliography}
%\newpage
%\bibliography{references}
%\bibliographystyle{ieeetr}

\end{document}
