\documentclass[preprint,12pt]{elsarticle}
\usepackage{graphicx}
\usepackage[margin=1.0in]{geometry}
\usepackage{color, colortbl}
\usepackage{hyperref}
\usepackage{float}
% \usepackage[affil-it]{authblk}
\usepackage{subcaption}
\newcommand{\note}[1]{\textcolor{blue}{#1}}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{LightRose}{rgb}{1,0.88,0.88}
\definecolor{LightGreen}{rgb}{0.88,1,0.88}

\title{Covolutionoal Auto-Encoders for Drift Chamber data de-noising for CLAS12}
\author[1]{Gagik Gavalian}
\author[2]{Polykarpos Thomadakis}
\author[2]{Angelos Angelopoulos}
\author[2]{Nikos Chrisochoides}
\author[3]{Raffaella De Vita}
%\author[1]{Veronique Ziegler}

% \affiliation[1]{organization={CRTC, Department of Computer Science, Old Dominion University}, city={Norfolk, VA}, country={USA}}
\address[1]{Jefferson Lab, Newport News, VA, USA}
\address[2]{CRTC, Department of Computer Science, Old Dominion University, Norfolk, VA, USA}
\address[3]{INFN, Sezione di Genova, 16146 Genova, Italy}
%Authored by Jefferson Science Associates, LLC under U.S. DOE Contract No. DE-AC05-06OR23177. The U.S. Government retains a non-exclusive, paid-up, irrevocable, world-wide license to publish or reproduce this manuscript for U.S. Government purposes.
%\fntext[fn1]{Authors contributed equally.}
%\fntext[fn2]{Correspoding author, \textit{gavalian@jlab.org}}

\begin{document}

%\begin{titlepage}
\begin{abstract}

In this article we present results of using Artificial Intelligence in CLAS12 tracking software. Several neural networks are used to aid tracking algorithms: drift chamber de-noising for background reduction, track candidate classification based on clusters in drift chamber regions and inefficiency recovery auto encoder. The implementation of neural networks in the data reconstruction workflow increased outcome of experimental measured quantities by $15-35\%$ for standard running conditions. Increase in statistics is equivalent of \$$8.3$M in experimental operation savings annually.

\end{abstract}
%\end{titlepage}
\maketitle


\input{introduction}

\input{data_description}

\input{data_analysis_dn}

\input{data_analysis_dn_ai}

\input{data_analysis_data}
%\input{results}

\input{summary}

\newpage

\section{Acknowledgments}

This material is based upon work supported by the U.S. Department of Energy, Office of Science,
Office of Nuclear Physics under contract DE-AC05-06OR23177, and NSF grant no. CCF-1439079 and
the Richard T. Cheng Endowment. The authors would like to thank Raffaella De Vita for help in
processing data with CLAS12 reconstruction software. This work was performed using the Turing
and Wahab computing clusters at Old Dominion University.
 
\newpage
\bibliography{references}
\bibliographystyle{ieeetr}

\end{document}
